---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
devtools::load_all()
```

# shinyVirga

<!-- badges: start -->
`r lifecycle::badge('experimental')`
<!-- badges: end -->

The goal of `shinyVirga` is to consolidate generalized utility functions useful in development of shiny apps that are currently used in the various Virga Labs repositories in one convenient location. `shinyVirga` is intended to supply Virga Labs developers with a toolkit of well-maintained functions and modules adaptable to various use cases encountered likely to be encountered during shiny development with Virga Labs. 


## Installation

You can install the development version of shinyVirga like so:

``` r
virgaUtils::install_virga("shinyVirga")
```
```{r, echo = FALSE}

get_rd_section <- function (rd_path) 
{
    rd <- rvest::read_html(glue::glue_collapse(capture.output(tools::Rd2HTML(rd_path))))
    out <- rvest::html_elements(rd, xpath = UU::xpath_sibling_between("h3[contains(text(), 'Description')]", following_sibling = "h3[contains(text(), 'Usage')]", preceding_sibling = "p")) |> 
      as.character()
    shiny::HTML(out)
}

```

The utility functions are divided into five categories (some functions overlap categories):

```{r, echo = FALSE, results='asis', warning=FALSE}

  purrr::map(rlang::set_names(c("General",
  "UI",
  "CSS",
  "JS",
  "Reactives",
  "golem")), ~{
  rlang::exec(htmltools::tags$ul,
    !!!functionMap::map_r_script(UU::dirs$R(glue::glue("utils_{tolower(.x)}"), ext = "R")) |> functionMap::functions() |> purrr::map(~{
      htmltools::tags$li(htmltools::tags$code(.x),": ", get_rd_section(fs::path("man", .x, ext = "Rd")) %|try|% NULL)
      })
  )
    
  }) |> named_to_li() |> htmltools::doRenderTags()

```
  
